---
title: "SLLIP_LENA_WC_data"
author: "JM Schneider"
date: "4/1/2020"
output: html_document
---
## The current script takes LENA snapshot data from the SLLIP project and re-organizes/summarizes it for subsequent data analyses. 

### Import libraries
```{r loadlib, echo=T, results='hide', message=F, warning=F}
library(psych)
library(readr)
library(optimx)
library(corrplot)
library(reshape)
library(reshape2)
library(lmerTest)
library(ggplot2)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(arm)
library(ez)
library(dplyr)
library(arm)
library(tidyr)
library(tidyverse)
```

### Load LENA data output as dataframe

```{r}
setwd("/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/")
df_hour=read.csv('LENAExport_Hourly_040120.csv')
df_overall=read.csv('LENAExport_Recordings_120320.csv')
```

### Clean the dataframe by removing unneccessary columns of data
```{r}
df_hour <- subset(df_hour, select = -c(ChildKey,RecordingDate,StartTime,EndTime,ProgramType,OrgID,GroupID,RecGroupID,ParticipantID,Recording.ID,HiddenRec,ExcludeFromAnalysis,FilteredRec,ErrorCodes,RecorderSerialNumber,ITS_File_Name,DatabaseInsertDateTime,RecorderTransferDateTime,Timezone))

df_overall <- subset(df_overall, select = -c(ChildKey,RecordingDate,StartTime,EndTime,ProgramType,OrgID,GroupID,RecGroupID,ParticipantID,Recording.ID,HiddenRec,ExcludeFromAnalysis,FilteredRec,ErrorCodes,RecorderSerialNumber,ITS_File_Name,DatabaseInsertDateTime,RecorderTransferDateTime,Timezone))
```

### Delete rows of repetitve data
```{r}
df_hour_clean <- df_hour %>% group_by(ExternalReferenceID) %>% top_n(1, AWC_COUNT)
df_overall_clean <- df_overall %>% group_by(ExternalReferenceID) %>% top_n(1, AWC_COUNT)
```

### Normalize three variables of interest: AWC, CV, CT
```{r}
df_hour_clean$AWC_COUNT_norm <- rescale(df_hour_clean$AWC_COUNT, binary.inputs="center")
df_hour_clean$CT_COUNT_norm <- rescale(df_hour_clean$CT_COUNT, binary.inputs="center")
df_hour_clean$CV_COUNT_norm <- rescale(df_hour_clean$CV_COUNT, binary.inputs="center")

df_overall_clean$AWC_COUNT_norm <- rescale(df_overall_clean$AWC_COUNT, binary.inputs="center")
df_overall_clean$CT_COUNT_norm <- rescale(df_overall_clean$CT_COUNT, binary.inputs="center")
df_overall_clean$CV_COUNT_norm <- rescale(df_overall_clean$CV_COUNT, binary.inputs="center")
```

### Compute Proportions
```{r}
df_overall_clean$AWC_prop<- (df_overall_clean$AWC_COUNT/df_overall_clean$Duration_Secs)
df_overall_clean$CT_prop<- (df_overall_clean$CT_COUNT/df_overall_clean$Duration_Secs)
df_overall_clean$CV_prop<- (df_overall_clean$CV_COUNT/df_overall_clean$Duration_Secs)
```

### Export data for later analysis
```{r}
write.csv(df_hour_clean, file = "/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/LENA_Cleaned_Hourly_040120.csv")
write.csv(df_overall_clean, file = "/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/LENA_Cleaned_Overall_120220.csv")
```

## Import Demographic Information
```{r}
df_dem_precovid=read.csv('/Volumes/data/projects/sllip/data/demographic/SLLIP _PreCOVID_Screener_12.03.csv')
df_dem_covid=read.csv('/Volumes/data/projects/sllip/data/demographic/SLLIP_Covid_Survey_12.03.csv')
df_dem<-dplyr::bind_rows(df_dem_precovid, df_dem_covid)
```

## Import Phone Screener Information
```{r}
df_phone=read.csv('/Volumes/data/projects/sllip/data/demographic/SLLIP_phonescreener_12-03.csv')
names(df_phone)[names(df_phone) == "record_id"] <- "ExternalReferenceID"
df_overall_clean$ExternalReferenceID<-str_remove(df_overall_clean$ExternalReferenceID,"sllip_00")
df_overall_clean$ExternalReferenceID<-str_remove(df_overall_clean$ExternalReferenceID,"sllip_0")
df_beh_lena <- merge(df_phone,df_overall_clean,by="ExternalReferenceID")
df_beh_lena_low <- df_beh_lena[which(df_beh_lena$free_reduced_lunch == 1),]
write.csv(df_beh_lena, file ="/Volumes/data/projects/sllip/data/demographic/SLLIP_phone_LENA_n18.csv" )
```

### Plotting preliminary data
```{r AWC, echo=FALSE}
plot(df_beh_lena_low$AWC_prop)
plot(df_beh_lena_low$CT_prop)
plot(df_beh_lena_low$CV_prop)

plot(df_beh_lena_low$AWC_COUNT_norm)
plot(df_beh_lena_low$CT_COUNT_norm)
plot(df_beh_lena_low$CV_COUNT_norm)

#df_beh_lena_low<- df_beh_lena_low[-c(6),]
pdf(file = '/Volumes/data/projects/sllip/analysis/R/Lena_output_fig.pdf')
df_beh_lena$NewReferenceID <- 1:18
df_beh_lena %>% group_by(NewReferenceID) %>%
  summarise(n=n(),
            AWC= AWC_COUNT_norm,
            CT = CT_COUNT_norm,
            CV = CV_COUNT_norm) %>% 
  gather("key", "value", - c(NewReferenceID, n)) %>%
  ggplot(aes(x = NewReferenceID, y = value, group = key, fill = key)) + geom_col()
dev.off()
```

## Rural versus Urban
```{r}
#df_beh_lena=read.csv('/Volumes/data/projects/sllip/data/demographic/SLLIP_phone_LENA.csv')

#df_beh_lena$AWC_COUNT_norm=as.character(as.numeric(df_beh_lena$AWC_COUNT_norm))
#df_beh_lena$Rural_Urban=as.character(as.numeric(df_beh_lena$Rural_Urban))

t.test(AWC_COUNT_norm~Rural_Urban, data = df_beh_lena)
t.test(CT_COUNT_norm~Rural_Urban, data = df_beh_lena)
t.test(CV_COUNT_norm~Rural_Urban, data = df_beh_lena)

myvars <- c("AWC_COUNT_norm", "CT_COUNT_norm", "CV_COUNT_norm", "Rural_Urban")
newdata <- df_beh_lena[myvars]

means<-aggregate(newdata,by=list(newdata$Rural_Urban),mean)
library(reshape2)
means.long<-melt(means,id.vars="Group.1")
means.long<-means.long[-c(7:8),]

pdf(file = '/Volumes/data/projects/sllip/analysis/R/Lena_output_rural_urban_fig.pdf')
ggplot(means.long,aes(x=variable,y=value,fill=factor(Group.1)))+
  geom_bar(stat="identity",position="dodge")+
  scale_fill_discrete(name="Location")+
  xlab("Quantity Type")+ylab("Normalized Quantity of Input")
dev.off()
```

