---
title: "SLLIP_LENA_WC_data"
author: "JM Schneider"
date: "4/1/2020"
output: html_document
---
## The current script takes LENA snapshot data from the SLLIP project and re-organizes/summarizes it for subsequent data analyses. 

### Import libraries
```{r loadlib, echo=T, results='hide', message=F, warning=F}
library(psych)
library(readr)
library(optimx)
library(corrplot)
library(reshape)
library(reshape2)
library(lmerTest)
library(ggplot2)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(arm)
library(ez)
library(dplyr)
library(arm)
```

### Load LENA data output as dataframe

```{r}
setwd("/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/")
df_hour=read.csv('LENAExport_Hourly_040120.csv')
df_overall=read.csv('LENAExport_Recordings_120320.csv')
```

### Clean the dataframe by removing unneccessary columns of data
```{r}
df_hour <- subset(df_hour, select = -c(ChildKey,RecordingDate,StartTime,EndTime,ProgramType,OrgID,GroupID,RecGroupID,ParticipantID,Recording.ID,HiddenRec,ExcludeFromAnalysis,FilteredRec,ErrorCodes,RecorderSerialNumber,ITS_File_Name,DatabaseInsertDateTime,RecorderTransferDateTime,Timezone))

df_overall <- subset(df_overall, select = -c(ChildKey,RecordingDate,StartTime,EndTime,ProgramType,OrgID,GroupID,RecGroupID,ParticipantID,Recording.ID,HiddenRec,ExcludeFromAnalysis,FilteredRec,ErrorCodes,RecorderSerialNumber,ITS_File_Name,DatabaseInsertDateTime,RecorderTransferDateTime,Timezone))
```

### Delete rows of repetitve data
```{r}
df_hour_clean <- df_hour %>% group_by(ExternalReferenceID) %>% top_n(1, AWC_COUNT)
df_overall_clean <- df_overall %>% group_by(ExternalReferenceID) %>% top_n(1, AWC_COUNT)
```

### Normalize three variables of interest: AWC, CV, CT
```{r}
df_hour_clean$AWC_COUNT_norm <- rescale(df_hour_clean$AWC_COUNT, binary.inputs="center")
df_hour_clean$CT_COUNT_norm <- rescale(df_hour_clean$CT_COUNT, binary.inputs="center")
df_hour_clean$CV_COUNT_norm <- rescale(df_hour_clean$CV_COUNT, binary.inputs="center")

df_overall_clean$AWC_COUNT_norm <- rescale(df_overall_clean$AWC_COUNT, binary.inputs="center")
df_overall_clean$CT_COUNT_norm <- rescale(df_overall_clean$CT_COUNT, binary.inputs="center")
df_overall_clean$CV_COUNT_norm <- rescale(df_overall_clean$CV_COUNT, binary.inputs="center")
```

### Compute Proportions
```{r}
df_overall_clean$AWC_prop<- (df_overall_clean$AWC_COUNT/df_overall_clean$Duration_Secs)
df_overall_clean$CT_prop<- (df_overall_clean$CT_COUNT/df_overall_clean$Duration_Secs)
df_overall_clean$CV_prop<- (df_overall_clean$CV_COUNT/df_overall_clean$Duration_Secs)
```

### Export data for later analysis
```{r}
write.csv(df_hour_clean, file = "/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/LENA_Cleaned_Hourly_040120.csv")
write.csv(df_overall_clean, file = "/Volumes/data/projects/sllip/data/mother-child_dyads/lena_output/LENA_Cleaned_Overall_120220.csv")
```

### Plotting preliminary data
```{r AWC, echo=FALSE}
plot(df_hour_clean$AWC_COUNT_norm)
plot(df_hour_clean$CT_COUNT_norm)
plot(df_hour_clean$CV_COUNT_norm)
```

